asc_file_database

### 2020-01-20 src/asc_file_database_combined_files.Rmd
splitting asc files - minor edits

asclayerall <- crossing(ascyears, ascmonths)
asclayerall$stackname <- paste0("st", asclayerall$ascyears, asclayerall$ascmonths) #this creates the name of the stack that will be used
asclayerall$temp_depth <- NA
asclayerall$chl_surface <- NA
asclayerall$o2_depth <- NA
asclayerall$salinity_depth <- NA
asclayerall$nao_sample <- NA
asclayerall$nao_prev <- NA
asclayerall$nao_winter <- NA
asclayerall$amo_sample <- NA
asclayerall$amo_winter <- NA

@@

asclayer <- subset(asclayerall, ascyears == myr)

@@

for (i in 1:nrow(asclayer)){
    print(asclayer$stackname[i])
    year <- asclayer$ascyears[i]
    month <- asclayer$ascmonths[i]

>>>>

asclayerall <- crossing(ascyearslist, ascmonths)
asclayerall$stackname <- paste0("st", asclayerall$ascyearslist, asclayerall$ascmonths) #this creates the name of the stack that will be used
asclayerall$temp_depth <- NA
asclayerall$chl_surface <- NA
asclayerall$o2_depth <- NA
asclayerall$salinity_depth <- NA
asclayerall$nao_sample <- NA
asclayerall$nao_prev <- NA
asclayerall$nao_winter <- NA
asclayerall$amo_sample <- NA
asclayerall$amo_winter <- NA

@@

asclayer <- subset(asclayerall, ascyearslist == myr)

@@

for (i in 1:nrow(asclayer)){
    print(asclayer$stackname[i])
    year <- asclayer$ascyearslist[i]
    month <- asclayer$ascmonths[i]

### 2020-01-20 src/comb-maxent.Rmd
splitting asc files - minor edits

select month
```{r month of interest -change}
mthna <- "apr"
mthno <- "4"
```

@@

  if (yr == "2001" | yr == "2006" | yr == "2007"){
    betaval <- 1.75
  } else if (yr == "2000"| yr == "2002" | yr == "2003" | yr == "2004"){
    betaval <- 2
  } else if (yr == "1999" | yr == "2005" | yr == "2008" | yr == "2009"){
    betaval <- 2.25
  } else if (yr == "2010" | yr == "2011"){
    betaval <- 2.5
  } else if (yr == "1998"){
    betaval <- 2.75
  }

@@

    yr <- as.numeric(yr)
 unlayer_yr <- subset(unlayer, ascyears == yr)
    #unlayer_yr <- unlayer_yr[-c(1), ]
    unlayer_yr[] <- lapply(unlayer_yr, as.character) #from https://stackoverflow.com/questions/2851015/convert-data-frame-columns-from-factors-to-characters
    stackdeplst <- list()
    stackdep <- subset(unlayer_yr, select = c(stackname))
    stackdeplst[[year]] <- stackdep
    write.csv(stackdep, paste0("../output/maxent/models/test-comb/", timeslice, "/stackdepthlist_", yr, ".csv"), row.names = FALSE)
    aea <- raster("../output/env/aea.tif")

@@

>>>>

select month
```{r month of interest -change}
mthna <- "dec"
mthno <- "12"
```

@@

  if (yr == "1998"){
    betaval <- 0.25
  } else if (yr == "2001"){
    betaval <- 0.75
  } else if (yr == "2002" | yr == "2003"| yr == "2004"| yr == "2006"| yr == "2011"){
    betaval <- 1
  } else if (yr == "2005"){
    betaval <- 1.25
  } else if (yr == "1999" | yr == "2000"| yr == "2009"){
    betaval <- 1.5
  } else if (yr == "2007"){
    betaval <- 1.75
  } else if (yr == "2010"){
    betaval <- 2
  } else if (yr == "2008"){
    betaval <- 2.25
  }

@@

    yr <- as.numeric(yr)
 unlayer_yr <- subset(unlayer, ascyearslist == yr)
    #unlayer_yr <- unlayer_yr[-c(1), ]
    unlayer_yr[] <- lapply(unlayer_yr, as.character) #from https://stackoverflow.com/questions/2851015/convert-data-frame-columns-from-factors-to-characters
    stackdeplst <- list()
    stackdep <- subset(unlayer_yr, select = c(stackname))
    stackdeplst[[year]] <- stackdep
    write.csv(stackdep, paste0("../output/maxent/models/test-comb/", timeslice, "/stackdepthlist_", yr, ".csv"), row.names = FALSE)
    aea <- raster("../output/env/aea.tif")

@@

all layers need to be spit in bash
